\chapter{Conclusion and Future Work}
\label{ch:conclusion}

%
% Section: Conclusion
%
\section{Conclusion}
\label{sec:conclusion:conclusion}
In conclusion, the idea behind using NFTs and Wallets in order to track user data is interesting. A large amount of data can be gathered on users by using NFTs and Wallets. By looking at a Wallet's transaction history, it can be determined who they are interacting with, what they may be interested in, what products they are buying, and to what time they are completing these purchases. The main benefit of Wallets is that all of this information is public knowledge.

However, while technically possible to implement, tracking user data with this method comes with flaws. As discussed in chapter \ref{ch:results}, there are several factors that need to be overcome before wide-spread use can be considered. The variety of information gathered is neither as large, nor as in depth. The high entry barrier and high gas prices needed to interact with the blockchain need to be overcome before wide-spread adoption can be considered.

This means that NFTs and Wallets are a good supplement to tracking user data with cookies, but they do not replace cookies. The full potential of this method remains unfulfilled thus far.



%
% Section: Future Work
%
\section{Future Work and Path Forward}
\label{sec:conclusion:futureWork}
This paper is just the first step in research towards the power of NFTs, other than leveraging them as a financial investment. It only scratches the surface of this topic and a deep-dive into the subject matter would require both more time and dedication.

More research in this subject area would be interesting to see. There are many questions still open at the end of this writing, such as:
\begin{itemize}
	\item \textit{How to calculate the required product price to justify the gas price?}
	\item \textit{How could potential changes in laws affect potential wide-spread adoption of this method?}
	\item \textit{How does the high entry barrier affect potential application of this method?}
\end{itemize}

Obviously this paper is not able to cover all of the above points. Many questions are still open, as there is a research gap surrounding this subject. Diving into any of the above subjects would achieve very interesting results which may have a big impact on the future of the web.

A Master's Thesis would allow for the necessary environment to analyze any of these subjects in more detail.