\chapter{Current State of the Art and Related Work}
\label{ch:SOTA}
This chapter takes a look at current literature in a similar area as well as existing companies developing products in this field.

%
% Section: State of the Art
%
\section{Current State of the Art}
\label{sec:sota:stateOfTheArt}
At the time of writing, research has yet to be conducted on how to mimic the functionality of cookies through cryptocurrency wallets and NFTs. There is an obvious research gap in this are. This paper attempts to fill that gap. 

Online Stores and NFTs / Wallets
How is user data typically tracked online? 
Are there already nfts, sites, and tools to track data using nfts? 
Challenge of high entry barrier with nfts and wallets. A lot of nec- essary know-how 


%
% Section: Related Work
%
\section{Related Work}
\label{sec:sota:relatedWork}
A plethora of relevant research has been conducted on cookies, including their privacy issues, and on wallets and NFTs. This paper aims to bring these two areas of research together to answer the question at hand.

% Cookies
\subsection{Cookies}
\label{sec:sota:cookies}
Todo

% NFTs and Web3
\subsection{NFTs and Web3}
\label{sec:sota:nfts}
Todo



%
% Section: Current Market Products
%
\section{Current Market Products}
\label{sec:sota:products}
Although no company openly speaks about acquiring data through wallets in order to learn more about their users, there are a handful of companies and products that make it possible to do so.

The following companies and products support the case study  of this paper (as will be mentioned in more detail later in section \ref{sec:methodology:caseStudy}).

% Wallet Connect
\subsection{Wallet Connect}
\label{sec:sota:walletConnect}
Wallet Connect \cite{walletConnect} is a company developing various open source products which allow dApps to connect to your wallet. At the time of writing, their portfolio includes 4 products. However, only the first product is so far released to the public.
\begin{itemize}
	\item Sign: A secure way to connect your wallet to dApps and make secure transactions between them. \cite{walletConnect}
	\item Auth: A single-sign on by connecting your wallet to dApps. This means that a user does not have to create an individual account for each platform. \cite{walletConnect}
	\item Chat: A wallet-to-wallet messaging system which writes to the blockchain. \cite{walletConnect}
	\item Push: A notification system which will send push notifications to your phone any time any activity is detected within your wallet. \cite{walletConnect}
\end{itemize}

% Meta Mask
\subsection{MetaMask}
\label{sec:sota:metaMask}



Especially relevant for this paper is any type of application or product that allows single-sign on for a dApp using a user's wallet. Section \ref{sec:methodology:caseStudy} will go into more detail on this.

